Arrival Management with Open Data

### 2023-04-05 paper.qmd
Update paper.qmd

This study builds on open trajectory data from Opensky Network. 
Opensky Network is a non-profit organisation and community-based surveillance data collection network. 
The collected air traffic data is available to researchers and government organisations on a license-free basis.
Performance monitoring is based on the principle of reproducibility and transparency. 
Open access to the underlying data and enrusing reproducibility of the analysis is a key requirement [@PRC_OPDI2022).

-   trajectory data - Opensky Network, weekly downloads
-   airport information - Openstreet Map

data downloaded & script development, data cleaning

>>>>

This study builds on open trajectory data from Opensky Network. 
Opensky Network is a non-profit organisation and community-based surveillance data collection network. 
The collected air traffic data is available to researchers and government organisations on a license-free basis.
Performance monitoring is based on the principle of reproducibility and transparency. 
Open access to the underlying data and enrusing reproducibility of the analysis is a key requirement [@PRC_OPDI2022].
For this feasibilty study we used a prepared download sample of the Opensky Network data comprising 10 days of operations in 2019 and 2022.

The airport information required for this study was derived from Openstreet Map and validated by publicly available AIP information.
Openstreet Map also builds on a community driven effort to provide accurate and timely maps. 
It revolves around seeing the public as a central source of geographical information and voluteering to its maintenance.
Over the past years, the information on airports has iteratively improved. 
The principal information required for this paper comrpised the aerodrome reference points and runway thresholds and associated elevations.

The primary input to this paper was the air traffic data downloaded from Opensky Network.
The following sections describe the data preparatory and analytical steps taken and motivates the chosen heuristics and approaches.
